COG-ED Manuscript

### 2021-11-03 06_Paper/COG-ED/Manuscript.Rmd
updated d prime calculation with trimmed RT data

  # set the number of targets and non-targets, so in case the paradigm will be changed it is easily accessible
  # they are multiplied by 2, because there are two runs per n-back level

  num_targets <- 16*2
  num_nontargets <- 48*2

@@

  levelindex <- c(1,which(data_nback$level != dplyr::lag(data_nback$level)),nrow(data_nback))

@@

    hits <- length(which(data_nback$target[c(levelindex[i]:(levelindex[i+1])-1)] == 1 &
                           data_nback$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1) + (levelindex[i]-1))
    falsealarms <- length(which(data_nback$target[c(levelindex[i]:(levelindex[i+1])-1)] == 0 &
                           data_nback$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 0) + (levelindex[i]-1))
    newdata <- data.frame(subject = data_nback$subject[levelindex[i]],
                          level = data_nback$level[levelindex[i]],
                          hitrate = hits/num_targets,
                          falsealarmrate = falsealarms/num_nontargets)
    dprime <- rbind(dprime, newdata)

@@

    meanrt <- mean(data_nback$rt[which(data_nback$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1)
                                 +(levelindex[i]-1)], na.rm = TRUE)

    newdata <- data.frame(subject = data_nback$subject[levelindex[i]],
                          level = data_nback$level[levelindex[i]],
                          meanrt = meanrt)
    rt <- rbind(rt, newdata)

@@

require(gtools)
demo_data = data.frame(level = rep(1:4,24))
sv = permutations(n = 4, r = 4, v = c(0.1,0.4,0.85,1))
m = 1
for (n in 1:(nrow(demo_data)/4)) {
  demo_data$subject[m:(m+3)] = rep(n,4)
  #demo_data$sv[m:(m+3)] = sv[n,]
  demo_data$sv[m:(m+3)] = sample(x = c(0.11,0.38,0.45,0.53,0.70,0.85,0.90,1.00), size = 4, replace = FALSE, prob = c(0.025,0.025,0.05,0.05,0.05,0.05,0.05,0.7))
  m = m + 4
}
subjectindex <- c(1,which(demo_data$subject != dplyr::lag(demo_data$subject)),nrow(demo_data))
demo_sv <- data.frame(subject = character(), auc_sv = double(),
                      ascent_mean = double(), ascent_sum = double(), auc_x_ascentmean = double(),
                      auc_westbrook = double())
for (i in 1:(length(subjectindex)-1)) {
  sv_sorted <- sort(demo_data$sv[subjectindex[i]:(subjectindex[i]+3)])
  newdata <- data.frame(subject = demo_data$subject[subjectindex[i]],
                        auc_sv = auc(demo_data$level[subjectindex[i]:(subjectindex[i]+3)], demo_data$sv[subjectindex[i]:(subjectindex[i]+3)],
                                   method = "trapezoid"),
                        auc_sv_sorted = (0.5 * (sv_sorted[1] + sv_sorted[2]) +
                                           0.5 * (sv_sorted[2] + sv_sorted[3]) +
                                           0.5 * (sv_sorted[3] + sv_sorted[4])),
                        ascent_mean = ((demo_data$sv[subjectindex[i]+3] - demo_data$sv[subjectindex[i]+2]) +
                                        (demo_data$sv[subjectindex[i]+2] - demo_data$sv[subjectindex[i]+1]) +
                                        (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]]))/3,
                        ascent_sum = (demo_data$sv[subjectindex[i]+3] - demo_data$sv[subjectindex[i]+2]) +
                                        (demo_data$sv[subjectindex[i]+2] - demo_data$sv[subjectindex[i]+1]) +
                                        (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]]),
                        auc_x_ascentmean = auc(demo_data$level[subjectindex[i]:(subjectindex[i]+3)], demo_data$sv[subjectindex[i]:(subjectindex[i]+3)],
                                               method = "trapezoid") * (((demo_data$sv[subjectindex[i]+3] - demo_data$sv[subjectindex[i]+2]) +
                                        (demo_data$sv[subjectindex[i]+2] - demo_data$sv[subjectindex[i]+1]) +
                                        (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]]))/3),
                        auc_westbrook = (0.5 * (sv_sorted[1] + sv_sorted[2]) +
                                           0.5 * (sv_sorted[1] + sv_sorted[3]) +
                                           0.5 * (sv_sorted[1] + sv_sorted[4]))/3)
  demo_sv <- rbind(demo_sv, newdata)
}
demo_cor <- cor(demo_sv$auc_sv, demo_sv$auc_westbrook)

@@

ggplot(demo_data[c((1*4+1):(1*4+4),(4*4+1):(4*4+4),(15*4+1):(15*4+4),(17*4+1):(17*4+4)),], aes(x=level, y=sv, group=subject)) +
  geom_line(aes(color=subject), size = 1.5, position = position_jitter(w = 0.03, h = 0.03))
ggplot(demo_data[c((3*4+1):(3*4+4),(5*4+1):(5*4+4),(9*4+1):(9*4+4),(11*4+1):(11*4+4)),], aes(x=level, y=sv, group=subject)) +
  geom_line(aes(color=subject), size = 1.5, position = position_jitter(w = 0.03, h = 0.03))
ggplot(demo_data[c((0*4+1):(0*4+4),(2*4+1):(2*4+4),(21*4+1):(21*4+4),(23*4+1):(23*4+4)),], aes(x=level, y=sv, group=subject)) +
  geom_line(aes(color=subject), size = 1.5, position = position_jitter(w = 0, h = 0.03))
```

>>>>

@@

  levelindex <- c(1,which(data_RT$level != dplyr::lag(data_RT$level)),nrow(data_RT))

@@

    # set the number of targets and non-targets
    num_targets <- length(which(data_RT$target[c(levelindex[i]:(levelindex[i+1])-1)] == 1))
    num_nontargets <- length(which(data_RT$target[c(levelindex[i]:(levelindex[i+1])-1)] == 0))

    hits <- length(which(data_RT$target[c(levelindex[i]:(levelindex[i+1])-1)] == 1 &
                           data_RT$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1) + (levelindex[i]-1))
    falsealarms <- length(which(data_RT$target[c(levelindex[i]:(levelindex[i+1])-1)] == 0 &
                           data_RT$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 0) + (levelindex[i]-1))
    newdata <- data.frame(subject = data_RT$subject[levelindex[i]],
                          level = data_RT$level[levelindex[i]],
                          hitrate = hits/num_targets,
                          falsealarmrate = falsealarms/num_nontargets)
    dprime <- rbind(dprime, newdata)

@@

    meanrt <- mean(data_RT$rt[which(data_RT$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1)
                                 +(levelindex[i]-1)], na.rm = TRUE)

    newdata <- data.frame(subject = data_RT$subject[levelindex[i]],
                          level = data_RT$level[levelindex[i]],
                          meanrt = meanrt)
    rt <- rbind(rt, newdata)

@@

require(gtools)
demo_data = data.frame(level = rep(1:4,24))
sv = permutations(n = 4, r = 4, v = c(0.1,0.4,0.85,1))
m = 1
for (n in 1:(nrow(demo_data)/4)) {
  demo_data$subject[m:(m+3)] = rep(n,4)
  #demo_data$sv[m:(m+3)] = sv[n,]
  demo_data$sv[m:(m+3)] = sample(x = c(0.11,0.38,0.45,0.53,0.70,0.85,0.90,1.00), size = 4, replace = FALSE, prob = c(0.025,0.025,0.05,0.05,0.05,0.05,0.05,0.7))
  m = m + 4
}
subjectindex <- c(1,which(demo_data$subject != dplyr::lag(demo_data$subject)),nrow(demo_data))
demo_sv <- data.frame(subject = character(), auc_sv = double(),
                      ascent_mean = double(), ascent_sum = double(), auc_x_ascentmean = double(), auc_x_ascentsum = double(),
                      auc_westbrook = double())
for (i in 1:(length(subjectindex)-1)) {
  sv_sorted <- sort(demo_data$sv[subjectindex[i]:(subjectindex[i]+3)])
  newdata <- data.frame(subject = demo_data$subject[subjectindex[i]],
                        auc_sv = auc(demo_data$level[subjectindex[i]:(subjectindex[i]+3)], demo_data$sv[subjectindex[i]:(subjectindex[i]+3)],
                                   method = "trapezoid"),
                        auc_sv_sorted = (0.5 * (sv_sorted[1] + sv_sorted[2]) +
                                           0.5 * (sv_sorted[2] + sv_sorted[3]) +
                                           0.5 * (sv_sorted[3] + sv_sorted[4])),
                        ascent_mean = ((demo_data$sv[subjectindex[i]+3] - demo_data$sv[subjectindex[i]+2]) +
                                        (demo_data$sv[subjectindex[i]+2] - demo_data$sv[subjectindex[i]+1]) +
                                        (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]]))/3,
                        ascent_sum = (demo_data$sv[subjectindex[i]+3] - demo_data$sv[subjectindex[i]+2]) +
                                        (demo_data$sv[subjectindex[i]+2] - demo_data$sv[subjectindex[i]+1]) +
                                        (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]]),
                        auc_x_ascentmean = auc(demo_data$level[subjectindex[i]:(subjectindex[i]+3)], demo_data$sv[subjectindex[i]:(subjectindex[i]+3)],
                                               method = "trapezoid") * (((demo_data$sv[subjectindex[i]+3] - demo_data$sv[subjectindex[i]+2]) +
                                        (demo_data$sv[subjectindex[i]+2] - demo_data$sv[subjectindex[i]+1]) +
                                        (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]]))/3),
                        auc_x_ascentsum = auc(demo_data$level[subjectindex[i]:(subjectindex[i]+3)], demo_data$sv[subjectindex[i]:(subjectindex[i]+3)],
                                               method = "trapezoid") * ((demo_data$sv[subjectindex[i]+3] - demo_data$sv[subjectindex[i]+2]) +
                                        (demo_data$sv[subjectindex[i]+2] - demo_data$sv[subjectindex[i]+1]) +
                                        (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]])),
                        auc_westbrook = (0.5 * (sv_sorted[1] + sv_sorted[2]) +
                                           0.5 * (sv_sorted[1] + sv_sorted[3]) +
                                           0.5 * (sv_sorted[1] + sv_sorted[4]))/3)
  demo_sv <- rbind(demo_sv, newdata)
}
demo_cor <- cor(demo_sv$auc_sv, demo_sv$auc_westbrook)

@@

#library(data.table) for the melt function
ggplot(melt(setDT(demo_sv), id.vars = "subject", variable.name = "measure"), aes(fill=measure,y=value,x=subject)) + geom_bar(position = "dodge", stat = "identity")
```
